\emph{Pick me, pick me!} she screamed silently.

The gorgeous lifeguard didn't. She sighed. The way he licked his lips while waiting in the line! He'd surely appreciate her curvy outlines. But no, he had to take one of those impish fork tarts with his fries.

She was patient though. It was a busy day. People queued even now when the sun was almost down. Her time would come.

Just before closing, a big family came. Their rowdy kids were fighting for the cutlery. She was smart and tiptoed to the front of the box, side-stepping hundreds of her kin. No way she would stay behind now.

Her move was perfectly orchestrated. She ended up among the chosen ones. The family left few smudgy notes on the till and flew her over to a wooden table nearby.

She lay trembling on a pile of napkins, both excited and fearful. The family gorged themselves on their greasy grub, washing it down with pints of melted sugar. Any minute now and a smooth dip would come, followed by an eager suck; the purpose of her life fulfilled!

Sadly, she flared up all for nothing. In the end, she was utterly forgotten. Another thing the people had to have but never really needed.

\vspace{0.5cm}

They were gone and the night was falling. Fresh breeze started to blow and lifted her off the table. She was dragged down the beach, bruising her delicate white skin on the sand.

She was about to die a virgin.

\emph{Is there a life after this misery?} she wondered. \emph{Am I going to a better place? Will there be anyone to ever care for me?}

With these thoughts, she was swept into the ocean.

And there, it was a different world entirely. If that was death, she never wanted to live again. The swell caressed her in ways no hand or tongue could ever match. There was a heavenly glow all around whenever she stirred. It was so easy to forget about all she knew and used to be during her rather long shelf life.

Soon she was spotted by dolphins that surfed waves breaking on an outer reef. They spent hours by taking her for exhilarating noserides through barrels lit by the rising moon.

The dolphins got bored eventually, but others kept her company after they'd left. Curious fish nibbled on her and algae made her a fancy veil. And when she'd learned all she could about the coastal waters, she set to sail the open seas, riding on currents full of other lost souls like her.

She saw wonders beyond all count, but the adventurous afterlife took its toll at last. The currents were wise though. They brought her, all frail, to a resting place.

Now she floats round and round, and slowly becomes one with the ocean. But don't you worry, she'll still be out there for many years to come. She's waiting for the whole world to waste away and join her in the plastic paradise.
